Robot Team III: Scotty Strikes Back

### 2024-04-10 paper/paper.tex
more annotation to bibliography

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % John
\newcommand{\orcidauthorB}{0000-0003-2688-648X} % Lakitha
\newcommand{\orcidauthorC}{0000-0002-9841-6703} % Shawhin
\newcommand{\orcidauthorD}{0000-0003-2657-3416} % Prabuddha
\newcommand{\orcidauthorE}{0000-0003-4265-9543} % David
\newcommand{\orcidauthorF}{0000-0003-0667-2345} % Ash
\newcommand{\orcidauthorG}{0000-0002-0126-218X} % Adam

% Authors, for the paper (add full first names)
% \Author{John Waczak \orcidA{}, Adam Aker \orcidG{}, Lakitha O. H. Wijeratne \orcidB{}, Shawhin Talebi \orcidC{}, Ashen Fernando \orcidF{}, Prabuddha M. H. Dewage \orcidD{}, Mazhar Iqbal, Matthew Lary, David Schaefer and David J. Lary *\orcidE{}}
\Author{John Waczak \orcidA{} and David J. Lary *\orcidE{}}

@@

% MDPI internal command: Authors, for metadata in PDF
% \AuthorNames{John Waczak, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, Matthew Lary, David Schaefer and David J. Lary}
\AuthorNames{John Waczak and David J. Lary}

% MDPI internal command: Authors, for citation in the left column
% \AuthorCitation{Waczak, J.; Aker, A.; Wijeratne, L.O.H.; Talebi, S.; Fernando, B.; Hathurusinghe, P.; Iqbal, M.; Lary, M.; Schaefer, D.; Lary, D.J.}
\AuthorCitation{Waczak, J.; Lary, D.J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
% \address[1]{%
% Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); pxh180012@utdallas.edu (P.M.H.D.); mazhar.iqbal@utdallas.edu (M.I.); MDL210001@utdallas.edu (M.L.); captdaveschaefer@gmail.com (D.S.)}

\address[1]{%
Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.);}
\corres{\hangafter=1 \hangindent=1.05em \hspace{-0.82em}Correspondence: {David.Lary@utdallas.edu}}

@@

2. HSI Size allows their incorporation onto drones

@@

5. Unsupervised classification techniques are nice however standard algorithms like k-means clustering require prior knowledge of the number of constituent endmembers and do not, in general, provide any interpretable relationship between classes e.g. how is class 1 more similar to class 2 than to class 10.

@@

@@

\subsection{Autonomous Robot Team}
\subsection{Data Collection and Pre-Processing}
\subsection{Generative Topographic Mapping}
\subsection{Image Segmentation with the Normalized Spectral Similarity Score}

@@

\begin{table}[H]
  \caption{The top 25 models from the hyperparameter search. A variety of GTM were trained to explore the the impact of varying m, $\alpha$, and s.\label{tab:hp-search}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{m} & \textbf{$\alpha$} & \textbf{s} & \textbf{k} & \textbf{BIC} & \textbf{AIC} \\
    \midrule
    14 & 0.1 & 1.0 & 32 & -1.918e8 & -1.926e8\\
    13 & 0.01 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    16 & 0.01 & 1.5 & 32 & -1.917e8 & -1.926e8\\
    14 & 10.0 & 1.0 & 32 & -1.917e8 & -1.924e8\\
    16 & 0.001 & 1.5 & 32 & -1.917e8 & -1.926e8\\
    13 & 1.0 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    13 & 10.0 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    14 & 0.001 & 1.5 & 32 & -1.916e8 & -1.924e8\\
    13 & 0.1 & 1.0 & 32 & -1.916e8 & -1.923e8\\
    14 & 0.01 & 1.0 & 32 & -1.916e8 & -1.924e8\\
    15 & 0.01 & 1.5 & 32 & -1.916e8 & -1.925e8\\
    14 & 0.01 & 1.5 & 32 & -1.916e8 & -1.923e8\\
    15 & 1.0 & 1.0 & 32 & -1.916e8 & -1.924e8\\
    18 & 0.01 & 1.5 & 32 & -1.916e8 & -1.928e8\\
    12 & 0.01 & 1.0 & 32 & -1.916e8 & -1.921e8\\
    15 & 0.01 & 0.5 & 32 & -1.915e8 & -1.924e8\\
    17 & 1.0 & 1.0 & 32 & -1.915e8 & -1.926e8\\
    16 & 0.1 & 1.0 & 32 & -1.915e8 & -1.925e8\\
    18 & 0.001 & 1.5 & 32 & -1.915e8 & -1.928e8\\
    13 & 0.001 & 1.0 & 32 & -1.915e8 & -1.922e8\\
    12 & 1.0 & 1.0 & 32 & -1.915e8 & -1.921e8\\
    17 & 0.001 & 1.5 & 32 & -1.915e8 & -1.926e8\\
    15 & 0.001 & 1.5 & 32 & -1.915e8 & -1.923e8\\
    15 & 10.0 & 1.0 & 32 & -1.915e8 & -1.923e8\\
    12 & 0.1 & 1.5 & 32 & -1.915e8 & -1.92e8\\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

>>>>

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5910-0183} % John
\newcommand{\orcidauthorB}{0000-0003-2688-648X} % Lakitha
\newcommand{\orcidauthorC}{0000-0002-9841-6703} % Shawhin
\newcommand{\orcidauthorD}{0000-0003-2657-3416} % Prabuddha
\newcommand{\orcidauthorE}{0000-0003-4265-9543} % David
\newcommand{\orcidauthorF}{0000-0003-0667-2345} % Ash
\newcommand{\orcidauthorG}{0000-0002-0126-218X} % Adam
% \newcommand{\orcidauthorH}{} % Gokul

% Authors, for the paper (add full first names)
\Author{John Waczak \orcidA{}, Adam Aker \orcidG{}, Lakitha O. H. Wijeratne \orcidB{}, Shawhin Talebi \orcidC{}, Ashen Fernando \orcidF{}, Prabuddha M. H. Dewage \orcidD{}, Mazhar Iqbal, Matthew Lary, David Schaefer, Gokul Balagopal, and David J. Lary *\orcidE{}}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{John Waczak, Adam Aker, Lakitha O. H. Wijeratne, Shawhin Talebi, Bharana Fernando, Prabuddha Hathurusinghe, Mazhar Iqbal, Matthew Lary, David Schaefer, Gokul Balagopal, and David J. Lary}

% MDPI internal command: Authors, for citation in the left column
 \AuthorCitation{Waczak, J.; Aker, A.; Wijeratne, L.O.H.; Talebi, S.; Fernando, B.; Hathurusinghe, P.; Iqbal, M.; Lary, M.; Schaefer, Balagopal, G.; D.; Lary, D.J.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
Hanson Center for Space Sciences, University of Texas at Dallas, Richardson, TX 75080, USA;  john.waczak@utdallas.edu (J.W.); adam.aker@utdallas.edu (A.A.); lhw150030@utdallas.edu (L.O.H.W.); shawhintalebi@gmail.com (S.T.); ashen.fernando@utdallas.edu  (B.F.); pxh180012@utdallas.edu (P.M.H.D.); mazhar.iqbal@utdallas.edu (M.I.); MDL210001@utdallas.edu (M.L.); captdaveschaefer@gmail.com (D.S.); gokul.balagopal@utdallas.edu (G.B.);}

@@

2. HSI Size allows their incorporation onto drones
    - \cite{robot-team-1}
    - \cite{robot-team-2}

@@

5. Unsupervised classification techniques are nice however standard algorithms like k-means clustering require prior knowledge of the number of constituent endmembers and do not, in general, provide any interpretable relationship between classes e.g. how is class 1 more similar to class 2 than to class 10. The Self Organizing map introduced by Kohonen is a popular technique which enables an unsupervised classification of data where classes

- We should make a note about Autoencoders and VAEs here. While they work well in many contexts, they do not provide a relationship between classes and there is no obvious way to choose the size of the encoding

@@

IDEA: spectral unmixing of water is challenging due to nonlinear effects of scattering by solids and absorption by dissolved chemicals (dyes etc...) this motivates a nonlinear approach to endmember identification, etc...

@@

\subsection{Autonomous Robot Team}
\subsection{Data Collection and Pre-Processing}
\subsection{Generative Topographic Mapping}

- GTM paper oricinal \cite{gtm-bishop-1}
- GTM developments paper \cite{gtm-biship-2}

\subsection{Image Segmentation with the Normalized Spectral Similarity Score}

@@

\begin{table}[H]
  \caption{The top 25 models from the hyperparameter search. A variety of GTM were trained to explore the the impact of varying m, $\alpha$, and s.\label{tab:hp-search}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{m} & \textbf{$\alpha$} & \textbf{s} & \textbf{k} & \textbf{BIC} & \textbf{AIC} \\
    \midrule
    14 & 0.1 & 1.0 & 32 & \textbf{-1.918e8} & -1.926e8\\
    13 & 0.01 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    16 & 0.01 & 1.5 & 32 & -1.917e8 & -1.926e8\\
    14 & 10.0 & 1.0 & 32 & -1.917e8 & -1.924e8\\
    16 & 0.001 & 1.5 & 32 & -1.917e8 & -1.926e8\\
    13 & 1.0 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    13 & 10.0 & 1.0 & 32 & -1.917e8 & -1.923e8\\
    14 & 0.001 & 1.5 & 32 & -1.916e8 & -1.924e8\\
    13 & 0.1 & 1.0 & 32 & -1.916e8 & -1.923e8\\
    14 & 0.01 & 1.0 & 32 & -1.916e8 & -1.924e8\\
    15 & 0.01 & 1.5 & 32 & -1.916e8 & -1.925e8\\
    14 & 0.01 & 1.5 & 32 & -1.916e8 & -1.923e8\\
    15 & 1.0 & 1.0 & 32 & -1.916e8 & -1.924e8\\
    18 & 0.01 & 1.5 & 32 & -1.916e8 & -1.928e8\\
    12 & 0.01 & 1.0 & 32 & -1.916e8 & -1.921e8\\
    15 & 0.01 & 0.5 & 32 & -1.915e8 & -1.924e8\\
    17 & 1.0 & 1.0 & 32 & -1.915e8 & -1.926e8\\
    16 & 0.1 & 1.0 & 32 & -1.915e8 & -1.925e8\\
    18 & 0.001 & 1.5 & 32 & -1.915e8 & -1.928e8\\
    13 & 0.001 & 1.0 & 32 & -1.915e8 & -1.922e8\\
    12 & 1.0 & 1.0 & 32 & -1.915e8 & -1.921e8\\
    17 & 0.001 & 1.5 & 32 & -1.915e8 & -1.926e8\\
    15 & 0.001 & 1.5 & 32 & -1.915e8 & -1.923e8\\
    15 & 10.0 & 1.0 & 32 & -1.915e8 & -1.923e8\\
    12 & 0.1 & 1.5 & 32 & -1.915e8 & -1.92e8\\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}
